---
title: "day8-activities"
format: html
editor: visual
---

## Task 1: 

```{r}
space_launches <- read_csv(here("data","space_launches.csv"))
```

```{r}
space_launches %>%
  filter(launch_year == 2009) %>% 
  ggplot(aes(y=fct_reorder(type,agency),x = agency)) +
  geom_point() +
  facet_wrap(~state_code, scale = "free") 
```

```{r}
san_francisco <- read_csv(here("data", "San_Francisco_Communitywide_Greenhouse_Gas_Inventory.csv")) %>%
  clean_names()
```

1.  Create a summary table of total annual greenhouse gas emissions (only from Emissions_mtCO2e column) by sector_general

    ```{r}
    san_francisco_year <- san_francisco %>%
      group_by(calendar_year, sector_general) %>%
      summarize(sum_of_emission = sum(emissions_mt_co2e))
    ```

2.  Create a summary table of total annual greenhouse gas emissions (only from Emissions_mtCO2e column) by year and commodity type

    ```{r}
    san_francisco_emission <- san_francisco %>% 
      group_by(calendar_year, commodity_type) %>% 
      summarize(mean = sum(emissions_mt_co2e), na.rm= TRUE)
    ```

3.  Create a subset of the data that only contains observations from 2005 on, only for observations where `Sector_Detail2` contains the pattern \"PG&E\", then limit to columns `Calendar_Year`, `Sector_Detail2` and `Emissions_mtCO2e`.

```{r}
SF_2005 <- san_francisco %>% 
  filter(calendar_year == 2005,str_detect(sector_detail2, pattern = "PG&E"))
```

```{r}
san_francisco_emission <- san_francisco %>% 
  group_by(calendar_year, sector_general) %>% 
  summarize(mean = sum(emissions_mt_co2e), na.rm= TRUE)

ggplot(san_francisco_emission, aes (x = calendar_year , y= mean)) +
  geom_line(aes(color = sector_general)) +
  labs(x="year", y= "emission (co2e)", title = "San Francisco emission") 
```

```{r}

```
