---
title: "Day8"
format: html
editor: visual
---

## Review basics of ggplot 

```{r}
library(tidyverse)
library(here)
library(janitor)

library(patchwork)
library(ggrepel)
library(gghighlight)
library(paletteer)
library(ggExtra)
library(ggbeeswarm)

```

## Read in data

```{r}
lizards <- read_csv(here::here("data_tidy","lizards.csv"))
```

Do some data wrangling to create a new subset from lizards where you :

1.  Limit the data to only contain western whiptails, colorado, checkered, and eastern fence lizards
2.  Add a new column with total length converted mm to cm
3.  Group by species and site
4.  Return a summary table with mean total length and standard deviation of total length by species and site

```{r}
length_table <- lizards %>% 
  filter(common_name %in% c("western whiptail", "colorado checkered", "eastern fence lizards")) %>%
  mutate(total_length_cm = total_length * 0.1) %>%
  group_by(common_name, site) %>%
  summarize(mean = mean(total_length_cm, na.rm= TRUE), std = sd(total_length_cm, na.rm = TRUE))
```

```{r}
ggplot (data=lizards, aes(x=total_length, y= weight)) +
  geom_point(aes(color= common_name))
```
