---
title: "Day8"
format: html
editor: visual
---

## Review basics of ggplot 

```{r}
library(tidyverse)
library(here)
library(janitor)

library(patchwork)
library(ggrepel)
library(gghighlight)
library(paletteer)
library(ggExtra)
library(ggbeeswarm)

```

## Read in data

```{r}
lizards <- read_csv(here::here("data_tidy","lizards.csv"))
```

Do some data wrangling to create a new subset from lizards where you :

1.  Limit the data to only contain western whiptails, colorado, checkered, and eastern fence lizards
2.  Add a new column with total length converted mm to cm
3.  Group by species and site
4.  Return a summary table with mean total length and standard deviation of total length by species and site

```{r}
length_table <- lizards %>% 
  filter(common_name %in% c("western whiptail", "colorado checkered", "eastern fence lizards")) %>%
  mutate(total_length_cm = total_length * 0.1) %>%
  group_by(common_name, site) %>%
  summarize(mean = mean(total_length_cm, na.rm= TRUE), std = sd(total_length_cm, na.rm = TRUE))
```

facet_wrap()

```{r}
ggplot (data=lizards, aes(x=total_length, y= weight)) +
  geom_point(aes(color= common_name)) +
  facet_wrap(~ common_name, scales = "free")
```

bar chart

```{r}
lizard_counts <- lizards %>% 
  dplyr::count(common_name)

#same : 
lizards %>% 
  group_by(common_name) %>%
  summarize(count =n())

# Use dplyr::count to find the total number of lizards by common name in the lizards dataset
```

```{r}
ggplot(data = lizard_counts, aes(x=n, y=fct_reorder(common_name, n))) +
  geom_col()
```

```{r}
ggplot (data=lizards, aes(x=total_length, y= weight, color = weight)) +
  geom_point() +
  scale_y_continuous(limits= c(0,100), 
                     breaks = seq(from = 0, to = 100, by = 20),
                     expand = c(0,20)) +
  scale_color_gradient(low = "red", high = "navy")
```
